%-------------------------
% Resume in Latex
% Author : Gennadii Chursov
% Based off of: https://github.com/sb2nov/resume and https://www.overleaf.com/latex/templates/jakes-resume/syzfjbzwjncs
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.6in} 
\addtolength{\textheight}{1.1in} 

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-4pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands with small gaps
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-1pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-3pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-3pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-3pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-2pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, itemsep=2pt, parsep=1pt, topsep=2pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[itemsep=1.5pt, parsep=1pt, topsep=1.5pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-3pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
%----------HEADING with Icons (compatible)----------
\begin{center}
    \textbf{\Huge \scshape Md. Abdullah Ibna Harun} \\[1pt]
    \small \textit{Software Quality Assurance Engineer} \\[3pt]
    \begin{tabular}{@{}p{0.48\textwidth} p{0.48\textwidth}@{}}
        \Mobilefone~+8801786287766 & LinkedIn: \href{https://www.linkedin.com/in/mdabdullahibnaharun}{linkedin.com/in/mdabdullahibnaharun} \\
        \Letter~\href{mailto:mdabdullahih13426@gmail.com}{mdabdullahih13426@gmail.com} & GitHub: \href{https://github.com/mdabdullahibnaharun}{github.com/mdabdullahibnaharun} \\
        \Mundus~20 Sukrabad, Dhaka-1207, Bangladesh & Portfolio: \href{https://mdabdullahibnaharun.github.io}{mdabdullahibnaharun.github.io} \\
    \end{tabular}
\end{center}


%-----------Objective-----------
\section*{Objective}
Software QA Engineer with 1.5+ years in manual and automated testing (Selenium, JMeter, JUnit, Postman). Experienced in bug tracking (Trello, Bitrix24), reducing post-release defects. Solved 300+ coding challenges. Certified in Software Testing and QA and Java Web Technologies. Seeking a full-time QA role.

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, itemsep=1pt, parsep=1pt, topsep=1pt, label={}]
    \small{\item{
     \textbf{Languages}: Java, Python, C, C++, SQL; 
     \textbf{Web/API}: Postman, REST APIs, Swagger; 
     \textbf{Testing}: Manual, Selenium, JMeter, JUnit; 
     \textbf{Version Control}: Git, GitHub; 
     \textbf{Databases}: MySQL, SQLite; 
     \textbf{Methodologies}: Agile, Waterfall, SDLC, STLC;
     \textbf{Documentation:} Technical Documentation, SRS, Testing Reports
     \textbf{Tools}: Trello, Bitrix24, Bugzilla, MS Teams
    }}
\end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

    \resumeSubheading
      {Smart Software Ltd.}{Feb 2024 -- Feb 2025}
      {Software QA Engineer}{Dhaka, Bangladesh}
      \resumeItemListStart
        \resumeItem{Performed manual and automated tests, led 4+ members, ensured on-time delivery of 200+ features.}
      \resumeItemListEnd

    \resumeSubheading
      {Creative Soft Technology Ltd.}{Sept 2023 -- Dec 2023}
      {SQA Engineer Intern}{Dhaka, Bangladesh}
      \resumeItemListStart
        \resumeItem{Tested \href{https://konnect.creativesofttechnology.com/}{Konnect Project} manually and automated, tracked bugs via Trello.}
      \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{Konnect Automation Testing (Selenium)} $|$ \emph{Java, Selenium, JUnit, Maven}}{Sept 2023 -- Dec 2023}
      \resumeItemListStart
        \resumeItem{Automated 50+ user actions, used Maven. \href{https://github.com/mdabdullahibnaharun/konnect-AutomationTesting-Selenium}{ GitHub link: https://github.com/mdabdullahibnaharun/konnect-AutomationTesting-Selenium}.}
      \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
    \resumeSubheading
      {Daffodil International University}{Dhaka, Bangladesh}
      {M.Sc. Software Engineering (Cybersecurity)}{Jul 2025 -- Running}
    \resumeSubheading
      {Daffodil International University}{Dhaka, Bangladesh}
      {B.Sc. CSE (CGPA: 3.78/4.00)}{Graduated Feb 2024}
\resumeSubHeadingListEnd

%-----------CERTIFICATIONS-----------
\section{Certifications}
\begin{itemize}[leftmargin=0.15in, itemsep=1pt, parsep=1pt, topsep=1pt, label={}]
    \small{\item{
     \textbf{Software Testing And Quality Assurance} – Skill Jobs (Dec 2023) \href{https://tinyurl.com/mdabihsqa}{Certificate: https://tinyurl.com/mdabihsqa} \\
     \textbf{Java From Basic To Professional} – PONDIT (Apr 2021) \href{https://tinyurl.com/mdabihjavabtop}{Certificate: https://tinyurl.com/mdabihjavabtop}
    \textbf{CyberSAFE} – BdREN (Apr 2023) \href{https://tinyurl.com/mdabihjavabtop}{Certificate: https://tinyurl.com/mdaihcybersafe}
    }}
\end{itemize}

%-----------EXTRA CURRICULAR ACTIVITIES-----------
\section{Activities}
\resumeSubHeadingListStart
    \resumeSubheading
      {DIU Student Prefect}{Jan 2021 -- Apr 2021}
      {Assisted in software testing and project labs}{Dhaka, Bangladesh}
    \resumeSubheading
      {Campus Ambassador – Show The Creativity}{Nov 2020 -- Jun 2021}
      {Managed team events and social media events}{Dhaka, Bangladesh}
\resumeSubHeadingListEnd
%-----------REFERENCES-----------
\section{References}
\begin{itemize}[leftmargin=0.15in, itemsep=1pt, parsep=1pt, topsep=1pt, label={}]
    \small{
    \item \textbf{Senjuti Ghosh} – SQA Engineer, Creative Soft Technology LTD. (Contact: +8801782760874)
    \item \textbf{Shah Nawaze Pavel} – CTO, Web Xpress (Contact: +8801711871722)
    \item \textbf{Mr. Saiful Islam} – Assistant Professor, Dept. of CSE, Daffodil International University (Contact: +8801989089279)
    }
\end{itemize}


%-------------------------------------------
\end{document}
